Surrogate Modelling of the Tritium Breeding Ratio

### 2020-06-21 talk_ucl_cdt_200622/adaptive.tex
Updates to adaptive slides.

        We developed a technique which is novel in the literature:
        \begin{itemize}
        \item Construct surrogate quality distribution by nearest- neighbour interpolation.
        \item Draw candidate samples by quality using MCMC.
        \item Include samples with high crowding distance.
        \item Repeat!
        \end{itemize}
      \column{6cm}
      \includegraphics[width=8cm]{qassplan}

@@

	\begin{columns}[T]
		\column{0.5\paperwidth}
		\vspace{0.5em}
		Evaluation performed both on the adaptively-sampled dataset and on a baseline uniform-random dataset.\newline

		An baseline scheme with incremental but uniform-random samples used as a placebo comparison.

@@

\begin{frame}
    \frametitle{Adaptive Sampling: Results}

    \begin{center}
    \includegraphics[width=12cm]{qassresult}
    \end{center}

@@

>>>>

        We developed a new technique:
        \vspace{-5pt}
        \begin{enumerate}
        \item Construct surrogate quality distribution by nearest- neighbour interpolation.
        \item Draw candidate samples by quality using MCMC.
        \item Include samples with high crowding distance.
        \item Repeat!
        \end{enumerate}
      \column{6cm}
      \includegraphics[width=8cm]{qassplan}

@@

	\begin{columns}[T]
		\column{0.5\paperwidth}
		\vspace{0.5em}
		Two evaluation sets:
		\begin{itemize}
		    \item Adaptively-sampled dataset
		    \item Independent random dataset
		\end{itemize}
		\vspace{15pt}

		Placebo comparison -- a baseline scheme without MCMC, incremental uniform-random samples.

@@

\begin{frame}
    \frametitle{Adaptive Sampling: Results}
    \vspace{-10pt}
    \begin{center}
    \includegraphics[width=12cm]{qassresult}
    \end{center}

    $60\%$ decrease in MAE for independent evaluation (dashed) \newline
    Equivalently, $6\%$ decrease in samples needed for same accuracy

@@

\begin{frame}
    \frametitle{Adaptive Sampling: Results}
    \vspace{-10pt}
    \begin{center}
    \includegraphics[width=12cm]{qassresult}
    \end{center}

    $60\%$ decrease in MAE for independent evaluation (dashed lines) \newline
    Equivalently, $6\%$ decrease in samples needed for same accuracy

\begin{frame}
    \frametitle{Adaptive Sampling: Results}
    \vspace{-10pt}
    \begin{center}
    \includegraphics[width=12cm]{qassincr}
    \end{center}

    Fewer incremented samples can lead to better accuracy! \newline
    But depends on initial samples, specific model -- further study needed.

### 2020-06-21 talk_ucl_cdt_200622/introduction.tex
Updates to adaptive slides.

\begin{frame}
	\frametitle{Problem Description}
	Breeding blankets convert neutron radiation from the fusion plasma into a steady supply of tritium fuel.
	\begin{align*}
		\isotope[1][0]{n} + \isotope[6][3]{Li} \rightarrow \isotope[3][1]{H} +
		\isotope[4][2]{He}
		\qquad\qquad
		\isotope[1][0]{n} + \isotope[7][3]{Li} \rightarrow \isotope[3][1]{H} +
		\isotope[4][2]{He} + \isotope[1][0]{n}
	\end{align*}
	However, the tritium breeding ratio (TBR) depends on numerous geometric and material parameters.\newline

	TBR evaluation \textit{Paramak} achieves very accurate results by OpenMC Monte Carlo neutronics simulation, but is computationally expensive.

@@

\begin{frame}
	\frametitle{Data Generation}
	We designed the Approximate TBR Evaluator (ATE) package to generate training and test datasets from Paramak.\newline
	 \begin{columns}[onlytextwidth,T]
      \column{\dimexpr\linewidth-6cm-5mm}

        UCL's Hypatia cluster provided the multithreading power for us to produce one million TBR samples, representing 27 days of runtime.\newline

        These runs included full evaluations on the 18 continuous and discrete parameters of Paramak, and "slice" evaluations with all discrete parameters frozen.

      \column{6cm}
      \vspace{0cm}
      \includegraphics[trim={0 0 0 2mm},clip,width=6cm]{params}

>>>>

\begin{frame}
	\frametitle{Problem Description}
	Tritium breeding blankets convert neutron radiation to tritium fuel:
	\begin{align*}
		\isotope[1][0]{n} + \isotope[6][3]{Li} \rightarrow \isotope[3][1]{H} +
		\isotope[4][2]{He}
		\qquad\qquad
		\isotope[1][0]{n} + \isotope[7][3]{Li} \rightarrow \isotope[3][1]{H} +
		\isotope[4][2]{He} + \isotope[1][0]{n}
	\end{align*}
	Tritium breeding ratio (TBR) = fuel bred / fuel consumed

	\begin{itemize}
	    \item Depends on numerous geometric and material parameters.
	    \item Evaluated precisely by OpenMC neutronics simulation \textit{Paramak}, but is computationally expensive. 
	\end{itemize}

@@

\begin{frame}
	\frametitle{Data Generation}
	We designed the Approximate TBR Evaluator (ATE) package to generate training and test datasets from Paramak.\newline
	 \begin{columns}[onlytextwidth,T]
      \column{\dimexpr\linewidth-7cm-5mm}

        Deployed Paramak on UCL's Hypatia cluster:
        \begin{itemize}
            \item Generated 1M samples
            \item 27 days of runtime
        \end{itemize}

        	\vspace{10pt}

        Two classes of runs:
        \begin{itemize}
            \item Full -- 18 discrete and continuous parameters
            \item Slice -- 11 continuous parameters
        \end{itemize}

      \column{7cm}
      \vspace{-0.5cm}
      \includegraphics[trim={0 0 0 2mm},clip,width=7cm]{params}
